\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref,color,amsmath}
\usepackage[bottom=.5pt,top=50pt,left=10pt,right=10pt]{geometry}

\begin{document}
	\centering
	\huge Fardin Jaman Aranyak\\
	\normalsize
	\textbf{(+880)1727957343} \textcolor{blue}{\url{https://github.com/Aronnok093}}\\
	\textbf{{E-Mail:190204093@aust.edu}}\\
	\raggedright\large \underline{\textbf{Experience:}}\\
	\quad\textbf{Program Manager Intern at Microsoft}, Dhaka, Bangladesh, 5/2018 – 8/2019
	I was in the team that was responsible for Microsoft Dynamics CRM, which is a piece of
	customer relationship management software. I led the effort to build a feature that allows users to
	easily keep track of business expenses. My responsibilities included the initial research, planning and
	managing the project, designing the feature, creating wireframes, and writing out our specs.\\
	\vspace{12pt}
	\quad\textbf{Data Science Intern at Microsoft},Dhaka,Bangladesh,6/2017 – 8/2017
	- Responsible for creating an internal dashboard tool. It is now used to view user
	engagement metrics such as the number of active users and the summary of their
	activities on the website I worked on.\\
	\vspace{12pt}
	\quad\textbf{Web Developer Intern at Daraz}, Dhaka,Bangladesh, 5/2016 – 8/2016\\
	\vspace{7pt}
	\large\underline{\textbf{Edducation:}} \\
	\quad\textbf{Ahsanullah University of Science and Technology},\\141 \& 142, Love Road, Dhaka 1208\\ \textbf{BSc In Computer Science and Engineering,} 2016\\
	\textit{CGPA.3.5}
	\vspace{7pt}\\
	\textbf{\underline{Tecnical Skill:}}\\
	\quad Experience in Product Management, Analytics/Statistics, and Software Engineering.
	Tools:\\
	\begin{itemize}
		\item Data Science: \textbf{R, Python with NumPy and Pandas, Spark (prior experience)}
		\item Programming Technologies:\textbf{SQL, MATLAB, Ruby, Ruby on Rails, Java, JavaScript,HTML/CSS}
	\end{itemize}
	\vspace{7pt}
	\large\textbf{\underline{Project:}}\\
	\quad\textbf{TELUS / IEEE Student Innovation Challenge,} September 2015
	At this technical product pitch contest, we presented an idea that helps blind and visually
	impaired individuals. Our idea was a device that converts 3-dimensional special information into
	sound. It would convert the proximity of the object in front of you to the loudness of the sound, and
	the height of the object to the pitch of the sound. We were awarded a \$3000 grant to develop a
	prototype for this idea, and we are currently in the process of developing it.\\
	\vspace{5pt}
	\quad\textbf{March Madness Prediction,} March 2014
	I made a least square model for predicting winners of March Madness, the national college
	basketball tournament in the United States. I built this model with different types of regularizations
	(L1 and L2), utilizing Python libraries such as NumPy and matplotlib. I ranked at the $32^{nd}$ place out
	of 248 teams at the Kaggle competition.\\
	
	
\end{document}